Model LF

### 2022-11-11 max_dp endogen stød.Rmd
Commit

COMMENT> 
BEHAVIORAL> prod_ds_sens
TSRANGE 2006 3 2020 1
EQ> TSDELTALOG(prod_ds_sens) =  pr_1* TSDELTALOG(wage_ds) +
pr_2* TSDELTALOG(TSLAG(y_ds,4)) +
pr_3* TSDELTALOG(y_ds) + 
pr_4* TSDELTALOG(TSLAG(wage_ds,1)) +
pr_8* LOG(TSLAG(y_ds,2))+
pr_9* LOG(TSLAG(dp_person,2))+
pr_10* LOG(TSLAG(prod_ds_sens,1))+
pr_11* LOG(TSLAG(wage_ds,2))
COEFF>  pr_1 pr_2 pr_3 pr_4 pr_8 pr_9 pr_10 pr_11
RESTRICT> pr_9 = 0.03
STORE> coe(223)

@@

```{r}
plot((unemp_05-unemp_bs56)*1000, col= "red")
```

@@

>>>>

COMMENT> 
BEHAVIORAL> prod_ds_sens
TSRANGE 2006 3 2020 1
EQ> TSDELTALOG(prod_ds_sens) =  pr_1* TSDELTALOG(wage_ds) +
pr_2* TSDELTALOG(TSLAG(y_ds,4)) +
pr_3* TSDELTALOG(y_ds) + 
pr_4* TSDELTALOG(TSLAG(wage_ds,1)) +
pr_8* LOG(TSLAG(y_ds,2))+
pr_9* LOG(TSLAG(dp_person,2))+
pr_10* LOG(TSLAG(prod_ds_sens,1))+
pr_11* LOG(TSLAG(wage_ds,2))
COEFF>  pr_1 pr_2 pr_3 pr_4 pr_8 pr_9 pr_10 pr_11
STORE> coe(223)

@@

@@

```{r}
plot(yk_ds_sbs3_low, col= "red"); lines(yk_ds, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```
